Network based multifactorial modelling microRNA-target interaction.

### 2019-05-26 article.Rmd
fix problematic reference moore

---
title: "Network based multifactorial modelling microRNA-target interaction."
author: 
- Selcen Ari^[Yildiz Technical University Department of Bioengineering]
- Alper Yilmaz^[Yildiz Technical University Department of Bioengineering]
date: "`r format(Sys.time(), '%d %B %Y')`"
output:
  pdf_document: 
  html_document: default
bibliography: ref.bib
---

@@

MicroRNAs (miRNAs) that are key regulator of gene expression through various post-transcriptional mechanisms are a family of short non-coding RNAs. Although repression mechanisms of miRNA are not fully understood, exact effect of miRNAs is regulation of direct target/targets negatively. Repressive activities of miRNAs vary depending on many factors that are significant to microRNA:target interactions. These factors include microRNA:target binding energy, binding location in target sequence, base pairing types between miRNA and target, abundance of miRNAs and targets [@grimson_microrna_2007]. Binding energies of miRNA:target complexes vary based on nucleotide context and determine folding stability of complex [@cao_predicting_2012]. It has been demonstrated that the binding energy between miRNA and target indicates stability or affinity of complex [@helwak_mapping_2013] and does not directly determine repressive activity of miRNA [@cao_predicting_2012]. Early studies have argued that 2-8 nt sequence, seed, located in miRNA 5’UTR bind to specific sequence located in 3’UTR of its target [@bartel_micrornas_2004; @lewis_conserved_2005]. In recent studies, it has been shown miRNAs can interact with targets via sequence that located in different region such as 5’UTR or CDS [@hausser_analysis_2013; @helwak_mapping_2013] **moore_mirnatarget_2015**. These studies also shown that binding location could indicate functionality of miRNA:target interaction or affect profile of target abundance. It has been shown that miRNAs exhibit repressive activity via, 6-8 nt long sequence that is prefectly complementary with targets, seed region at the 5’UTR of miRNAs [@bartel_micrornas:_2009; @grimson_microrna_2007]. On the other hand, some researchers have reported that seed sequence of miRNA can have mismatches or bulged/wobble nucleotides and locates in different region of miRNAs [@hafner_transcriptome-wide_2010; @helwak_mapping_2013]. In addition to all of these, abundance of miRNAs and targets and miRNA:target ratio in cells are determinant for efficiency of miRNA:target interaction [@arvey_target_2010; @bosson_endogenous_2014; @denzler_assessing_2014].

>>>>

---
title: "Network based multifactorial modelling microRNA-target interaction."
author: 
- Selcen Ari^[Yildiz Technical University Department of Bioengineering]
- Alper Yilmaz^[Yildiz Technical University Department of Bioengineering]
date: "`r format(Sys.time(), '%d %B %Y')`"
output:
  pdf_document: 
    keep_tex: true
  html_document: default
bibliography: ref.bib
---

@@

MicroRNAs (miRNAs) that are key regulator of gene expression through various post-transcriptional mechanisms are a family of short non-coding RNAs. Although repression mechanisms of miRNA are not fully understood, exact effect of miRNAs is regulation of direct target/targets negatively. Repressive activities of miRNAs vary depending on many factors that are significant to microRNA:target interactions. These factors include microRNA:target binding energy, binding location in target sequence, base pairing types between miRNA and target, abundance of miRNAs and targets [@grimson_microrna_2007]. Binding energies of miRNA:target complexes vary based on nucleotide context and determine folding stability of complex [@cao_predicting_2012]. It has been demonstrated that the binding energy between miRNA and target indicates stability or affinity of complex [@helwak_mapping_2013] and does not directly determine repressive activity of miRNA [@cao_predicting_2012]. Early studies have argued that 2-8 nt sequence, seed, located in miRNA 5’UTR bind to specific sequence located in 3’UTR of its target [@bartel_micrornas_2004; @lewis_conserved_2005]. In recent studies, it has been shown miRNAs can interact with targets via sequence that located in different region such as 5’UTR or CDS [@hausser_analysis_2013; @helwak_mapping_2013; @moore_mirnatarget_2015]. These studies also shown that binding location could indicate functionality of miRNA:target interaction or affect profile of target abundance. It has been shown that miRNAs exhibit repressive activity via, 6-8 nt long sequence that is prefectly complementary with targets, seed region at the 5’UTR of miRNAs [@bartel_micrornas:_2009; @grimson_microrna_2007]. On the other hand, some researchers have reported that seed sequence of miRNA can have mismatches or bulged/wobble nucleotides and locates in different region of miRNAs [@hafner_transcriptome-wide_2010; @helwak_mapping_2013]. In addition to all of these, abundance of miRNAs and targets and miRNA:target ratio in cells are determinant for efficiency of miRNA:target interaction [@arvey_target_2010; @bosson_endogenous_2014; @denzler_assessing_2014].
